\documentclass[a4paper]{article} 
\input{head}
\begin{document}

%-------------------------------
%	TITLE SECTION
%-------------------------------

\fancyhead[C]{}
\hrule \medskip % Upper rule
\begin{minipage}{0.295\textwidth} 
\raggedright
\footnotesize
Ketlin de Mello Moreira \hfill\\   
CCI Program\hfill\\
ketlindemello@gmail.com
\end{minipage}
\begin{minipage}{0.4\textwidth} 
\centering 
\large 
Summaries of Potential Projects\\ 
\normalsize 
IDEAD-ECP/PSIP\\ 
\end{minipage}
\begin{minipage}{0.295\textwidth} 
\raggedleft
\today\hfill\\
\end{minipage}
\medskip\hrule 
\bigskip

%-------------------------------
%	CONTENTS
%-------------------------------

\section{First Summary}
\textbf {What: In what project types PSIP will not the best approach?} \par
\textbf {Why: } \par
\textit{I want to study ways to improve and, possible correct bottlenecks in the PSIP project, by building a resource guide for teams, on how to address key problems during project improvements, because this information will help teams to find the best approach for their projects while avoiding possible roadblocks. I will probably find a pattern of approaches to be avoided and approaches to be adopted.}

%------------------------------------------------

\section{Second Summary}
\textbf {What: How well PTCs work with teams, agile processes, and issue tracking systems?} \par
\textbf {Why: To exemplify how  adapt the PSIP approach to other methods of project management, as Kanban, scrum, Agile.} \par
\textit{I want to study ways to adapt the PSIP approach to current software development project tracking systems, by analyzing data provided by teams that used PSIP before, because this information may help other teams to understand better the process of PSIP and its benefit when used along current methodologies.}

%-------------------------------

\section{Third Summary}
\textbf {What: What issues are being best addressed through the use of PTCs?} \par
\textbf {Why: A pattern can be used to guide other teams facing the same problem.} \par
\textit{I want to study the methodologies used to implement PTCs and what are their outcomes, by studying past projects and uploaded PTCs by teams that used the approach, because this information will help us to understand and offer a complete training to PSIP facilitators, as well as help organize the PTCs catalogue by issues.}



%------------------------------------------------

\end{document}
